---
title: "Reproducible figures for github"
date: "2023-12-08"
output: html_document
---

QUESTION 2


INTRODUCTION

I have already loaded the data into R. These steps will help me clean the data:

```{r}
data("penguins")
head(penguins)
summary(penguins)
library(palmerpenguins)
library(ggplot2)
```

```


```{r}
clean_column_names<- function(penguins_data)
  penguins_data%>%
    select(-starts_with("Delta"))%>%
    select(-Comments) %>%
    clean_names()
```

```{r}
remove_empty_columns_rows <- function(penguins_data)
    penguins_data %>%
        remove_empty(c("rows", "cols"))
```

HYPOTHESIS
Null hypothesis: There is no statistically significant relationship between body mass and bill depth in the species of penguins samples in the "penguins" dataset.
Alternative hypothesis: There is a relationship between body mass and bill depth. Bill depth increases/decreases with body mass.

FIGURE
```{r}
ggplot(penguins, aes(x= body_mass_g, y = bill_depth_mm, color=species)) +
  geom_point(position = position_jitter(width = 0.2, height = 0), size = 3) +
  labs(title = "Individual Bill Lengths by Species",
       x = "Body Mass (mm)",
       y = "Bill Depth (g)") +
  theme_minimal()+
  ggtitle("Scatter Plot representing bpdy mass and bill depth")
```

STATISTICAL TEST

```{r}
model <- lm(bill_depth_mm ~ body_mass_g, data = penguins)

# Using linear regression to compar ethe variables
summary(model)
```


Call:
lm(formula = bill_depth_mm ~ body_mass_g, data = penguins)

Residuals:
    Min      1Q  Median      3Q     Max 
-3.7437 -1.2235 -0.0116  1.2326  4.3468 

Coefficients:
              Estimate Std. Error t value Pr(>|t|)    
(Intercept) 22.0339465  0.5036206   43.75   <2e-16 ***
body_mass_g -0.0011621  0.0001177   -9.87   <2e-16 ***
---
Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1

Residual standard error: 1.744 on 340 degrees of freedom
  (2 observations deleted due to missingness)
Multiple R-squared:  0.2227,	Adjusted R-squared:  0.2204 
F-statistic: 97.41 on 1 and 340 DF,  p-value: < 2.2e-16

```{r}
ggplot(penguins, aes(x = body_mass_g, y = bill_depth_mm)) +
  geom_point() +  # Add points
  geom_smooth(method = "lm", se = FALSE, color = "blue") +  # Add linear regression line
  labs(title = "Linear Regression: Body Mass vs Bill Depth",
       x = "Body Mass (g)",
       y = "Bill Depth (mm)") +
  theme_minimal()
```


Figure2: This results figure shows the line of linear regression through the scatterplot. It is evident that the species that have a higher body mass tend to have a lower bill depth. However, within a species, the bill depth seems to be increasing with body mass. 

RESULTS AND DISCUSSION

Interpretation of the linear regression test:

1. Coefficients: 22.0339465 is the Y intercept. This means that 22.0339465 mm represents the value of bill depth when body mass if 0. 

-0.0011621 will be "m" in the equation mx+c=y. This means that as body mass increases by one gram, the bill length decreases by body_mass_g increases by one gram, the bill_depth_mm is expected to decrease by approximately 0.0011621 units.

2. Both coefficients are highly statistically significant. This is because the p-value (<2e-16) is very low.

3. The multiple R-squared value is 0.2227. This represents the proportion of the variance in bill depth that is explained by the model. Based on this, we can say that about 22.27% of the variability in bill depth is explained by the linear relationship with body mass.

CONCLUSION
This analysis shows that there is a significant negative relationship between body mass and bill length. This means that, as body mass increases, bill length tends to decrease. 

This is not what I expected as I had assumed a greater body mass would be linked to a more calorific diet. A greater bill depth could help the penguins catch bigger fish and therefore provide more nutrition for less time spent hunting. 
